Extended Data

### 2022-02-24 doc/manuscript/Dow_Extended_Data.Rmd
add row in edt2 for growth
@teixeirak  Any opposition to adding this row to EDT2? Now that tot growth is significant, we should add the values to one of our tables. This seems like the best one.

```{r mean_growth_parameters_table,  eval=TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
mean_growth_parameters <- read.csv("tables_figures/phenology_parameters.csv",  col.names = c("", "ring-porous","diffuse-porous","ring-porous", "diffuse-porous"), stringsAsFactors = FALSE, check.names = FALSE)
kable(mean_growth_parameters, caption = mean_growth_parameters_caption ,  format = "latex", booktabs = TRUE,  escape = F) %>%
add_header_above(c(" ",  "SCBI" = 2, "Harvard Forest"=2 )) %>%
    column_spec(1, width = "4cm") %>%
    pack_rows("Stem Growth", 2, 7, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
    pack_rows("Canopy Foliage (ecosystem level)", 8, 11, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
    pack_rows("Phenological temperature sensitivity* (days/°C)", 12, 20, latex_gap_space = "1em", colnum = 5, hline_before = FALSE) %>%
    add_indent(13:15)%>%
    add_indent(17:20)%>%
kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```
*Phenological temperature sensitivity refers to the sensitivity of a parameter to the mean maximum temperature ($T_{max}$) during the critical temperature window (Fig. 1). Because leaf phenology measurements were derived from satellite imagery and included both ring- and diffuse-porous trees, the selection of a critical window was less straightforward. We used the critical window which had the greatest correlation with leaf greenup timing as the critical window for leaf phenology calculations.

>>>>

```{r mean_growth_parameters_table,  eval=TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
mean_growth_parameters <- read.csv("tables_figures/phenology_parameters.csv",  col.names = c("", "ring-porous","diffuse-porous","ring-porous", "diffuse-porous"), stringsAsFactors = FALSE, check.names = FALSE)
kable(mean_growth_parameters, caption = mean_growth_parameters_caption ,  format = "latex", booktabs = TRUE,  escape = F) %>%
add_header_above(c(" ",  "SCBI" = 2, "Harvard Forest"=2 )) %>%
    column_spec(1, width = "4cm") %>%
    pack_rows("Stem Growth", 2, 7, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
    pack_rows("Canopy Foliage (ecosystem level)", 8, 11, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
    pack_rows("Temperature sensitivity* (days/°C)", 12, 20, latex_gap_space = "1em", colnum = 5, hline_before = FALSE) %>%
    add_indent(13:16)%>%
    add_indent(18:21)%>%
kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```
*Temperature sensitivity refers to the sensitivity of a parameter to the mean maximum temperature ($T_{max}$) during the critical temperature window (Fig. 1). Because leaf phenology measurements were derived from satellite imagery and included both ring- and diffuse-porous trees, the selection of a critical window was less straightforward. We used the critical window which had the greatest correlation with leaf greenup timing as the critical window for leaf phenology calculations.
